Assignment 5

### 2015-03-03 rmtw/a5/latex8.tex

In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}. These forms will be created and the pilot tested by the researchers taking part in the study. This allows the researchers to discover potential issues before the study takes place, such as ambiguity the data form questions.

The data extraction will be performed by both researchers on each individual study, meaning each study is extracted twice. By doing this, the chance for bias and misinterpretation is reduced. As suggested by kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data. In the case of duplication, the most robust study will be chosen.

@@

Data synthesis x

>>>>

\item Data extraction and monitoring (6.4) x

In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{keele2007guidelines}. These forms will be created and the pilot tested by the researchers taking part in the study. This allows the researchers to discover potential issues before the study takes place, such as ambiguity of questions in the form.

The data extraction will be performed by both researchers on each individual study, meaning each study is extracted twice. By doing this, the chance for bias and misinterpretation is reduced. As suggested by Kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data. In the case of duplication, the most robust study will be chosen.

@@

\item Data synthesis x

We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.

If we do, we'll need a sensitivity analysis to

\end{itemize}

\SubSection{Reporting (probably skip)}
\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)

Difficult to say which to use when the study has not been performed.

As the the results will be intended to have some impact upon whether or not MDSD is adopted in practice. As such the results will ideally be disseminated via journals, publications and via web pages to reach a broad audience.

\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}
